Network Origins of Social Distinction

### 2025-07-19 manuscript.tex

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/star.png}
            \caption{Star Graph}
            \label{fig:star}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
            \caption{Structural Fold}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/intra.png}
            \caption{2-Connected Subgraphs}
            \label{fig:intra}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/inter.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:inter}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/circle.png}
            \caption{Circle Graph}
            \label{fig:circle}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-one.png}
            \caption{Circle with Pendant}
            \label{fig:circleplus}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/clique.png}
            \caption{Clique Graph}
            \label{fig:clique}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/kite.png}
            \caption{Kite Graph}
            \label{fig:kite}
    \end{subfigure}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
    \label{fig:toys}
\end{figure}

@@

NOTES FROM 7|19|25 Meeting
***Triadic closure as distinction maximization*** 
Strogatz is random, preferential attachment of closure
Status homophilous (enh) attachment vs preferential vs random 
I wonder how much of balance theory is really just distinction maximization?
Non psychological theory polarity

3 versions
-Psychology
-Polarity 
-Status distinction

*Tie that cuts the longest shortest path Science, 
https://www.science.org/doi/full/10.1126/science.aau9735
Distinction homophily, chicken or egg of

>>>>

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/star.png}
            \caption{Star Graph}
            \label{fig:star}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sf.png}
            \caption{Structural Fold}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/intra.png}
            \caption{2-Connected Subgraphs}
            \label{fig:intra}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/inter.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:inter}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/circle.png}
            \caption{Circle Graph}
            \label{fig:circle}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-triangle.png}
            \caption{Circle Graph with Closure}
            \label{fig:circleplus}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/circle-plus-long.png}
            \caption{Circle Graph with Long Tie}
            \label{fig:circleplus}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/clique.png}
            \caption{Clique Graph}
            \label{fig:clique}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/kite.png}
            \caption{Kite Graph}
            \label{fig:kite}
    \end{subfigure}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
    \label{fig:toys}
\end{figure}

@@

%NOTES FROM 7|19|25 Meeting
%***Triadic closure as distinction maximization*** 
%Strogatz is random, preferential attachment of closure
%Status homophilous (enh) attachment vs preferential vs random 
%I wonder how much of balance theory is really just distinction maximization?
%Non psychological theory polarity

%3 versions
%-Psychology
%-Polarity, valenced ties 
%-Status distinction

%*Tie that cuts the longest shortest path Science, 
%https://www.science.org/doi/full/10.1126/science.aau9735
%Distinction homophily, chicken or egg of
